---
title: "Add Unique IDs to the shpFiles "
output: pdf_document
---
```{r}
require(rgdal)
require(tidyverse)
require(spdplyr)
```


## 1) Shruti Line

```{r}
# ran on 2/8/2021
sFL <- list.files("./Output/Vector/00_editTrainTest/ShrutiExtra", pattern = ".shp$",full.names = T)
lF <- str_subset(sFL, "LineData")
lineShp <- readOGR(lF) %>%
    mutate(shpSource = "shrutiAddLine_edit",
           sLineID = 1:15)
  
#shruti extra directory
outShr <- "./Output/Vector/00_editTrainTest/ShrutiExtra" 

# writeOGR(lineShp,outShr, "Delta_201910_LineData_nudged_SK_editV2", driver = "ESRI Shapefile", overwrite_layer=T) 
# note that without V2 is the same, but V2 was added so they could all be run on the same list patternv
```


We are deciding not to extract any of the other places from shruti though and just using those places that are related to cstars for soil and npv and what mui provided 
should we even bother extracting your EMR and SAV when we are not really using them?
The CSTARS_Poly_soil_NPV_water should only have the filtered areas, but not the required edits 

```{r}
sL <- list.files("./Output/Vector/00_editTrainTest", pattern = "_edit.shp$", recursive = T, full.names = T)
sL <- str_subset(sL, "ShrutiExtra", negate = T)
outDir <- "./Output/Vector/00_editTrainTest/version2"
for (s in sL){
  # read in shapefile
  shp <- readOGR(s) %>% 
    # add in an ca 
    mutate(pointID = 1:nrow(.))

  bn <- paste0(str_extract(s, "(?=[^\\\\|/]*$)(.)+(?=\\.)"), "V2")
  writeOGR(shp, dsn = outDir, layer = bn, driver = "ESRI Shapefile", overwrite_layer = T)
}

```


## for easy viewing 3/2
I think it makes sense to use the spring ones for all the spring files
test on 2018.
Want to check if you should use the spring file or the fall file. 
So open the closest 2018 spring file and look at it for both SAV and FLT 
```{r}
outDir <- "./Output/Vector/00_editTrainTest/view"
```

2019 
# SAV
```{r}
spr19 <- readOGR("./Output/Vector/00_editTrainTest/version2/Spring2019_editV2.shp")
savSpr19 <- spr19 %>% filter(str_detect(Species_1, "SAV"))
writeOGR(savSpr19, outDir, "Spring2019_editV2_sav", driver = "ESRI Shapefile")
```

# filter 2019 spring sav for the ones mui actually selected 
```{r}
savSpr19_fil <- spr19 %>% filter(str_detect(Species_1, "SAV")) %>% filter(X_20190425 == 1)
writeOGR(savSpr19_fil, outDir, "Spring2019_editV2_savFil", driver = "ESRI Shapefile")
```

2018 
#### 2018 sav 
```{r}
fall18 <- readOGR("./Output/Vector/00_editTrainTest/version2/fall2018_editV2.shp")
savfall18 <- fall18  %>% filter(str_detect(Species_1, "SAV"))
writeOGR(savfall18, outDir, "fall2018_editV2_sav", driver = "ESRI Shapefile", overwrite_layer = T)
```
# filter 2018 sav for the ones mui actually selected 
```{r}
savfall18_fil <- fall18 %>% filter(str_detect(Species_1, "SAV")) %>% filter(X_20181007 == 1)
writeOGR(savfall18_fil, outDir, "fall2018_editV2_savFil", driver = "ESRI Shapefile", overwrite_layer = T)
```

```{r}
fall17 <- readOGR("./Output/Vector/00_editTrainTest/version2/fall2017_editV2.shp")
savfall17 <- fall17 %>% filter(str_detect(Species_1, "SAV"))
outDir <- "./Output/Vector/00_editTrainTest/view"
writeOGR(savfall17, outDir, "fall2017_editV2_sav", driver = "ESRI Shapefile", overwrite_layer = T)
```

Both have good locations for SAV, so I would keep both of them 
- what are we deciding here again 
if we want to use the filter mui column for the fall or spring 

Do you want to do the same for fall, or are there just way too many points?


How many points are not there in the fall, but are there in the spring?


```{r}
fall19 <- readOGR("./Output/Vector/00_editTrainTest/version2/fall2019_editV2.shp")

fallFil <- fall19@data %>% 
  filter(X_20190425 != 0 & X_20191002 == 0) %>%
   as_tibble()
```
There are 8 points from the fall dates that mui said were in the 
